---
title: "README"
output:
  md_document:
    variant: markdown_github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# USC SDGmap R Package

Peter Wu at Carnegie Mellon was the inspiration of this project, and his original R package can be found on [Github](https://github.com/pwu97/SDGmapR). 
At USC, Brian Tinsley and Julie Hopper in the Office of Sustainability have been working to develop this package further and raise sustainability awareness in higher education.

The goal of `SDGmapR` is to provide an open-source foundation for the systematic mapping
to the United Nations Sustainable Development Goals (SDGs). In this R package one can find publicly available [SDG keyword datasets](https://github.com/USC-Office-of-Sustainability/USC-SDGmap/tree/main/Keyword%20Lists) in the `tidy` data format, the [UN Official SDG color scheme](https://www.un.org/sustainabledevelopment/wp-content/uploads/2019/01/SDG_Guidelines_AUG_2019_Final.pdf) and several functions related to the mapping of text to particular sets of keywords.

## Installation

You can install the development version from [Github](https://github.com/USC-Office-of-Sustainability/USC-SDGmap) with:

```{r}
# install.packages("devtools")
# devtools::install_github("USC-Office-of-Sustainability/USC-SDGmap")
```

## Publicly Available SDG Keywords

The table below lists publicly available SDG keywords that have been published online. For this package, we used the CMU250 keyword list combined with some words from USC's Presidental Working Group (PWG) keyword list which mapped to the CMU1000 keyword list. Instructions for how to update or create your own keyword list will be described later in this readme... 
<!-- add a link here -->

```{r, echo=FALSE, example}
library(knitr)
sdg_table <- data.frame(
  "Source" = c("[USC-CMU keyword list](www.google.com)", 
               "[Core Elsevier (Work in Progress)](https://data.mendeley.com/datasets/87txkw7khs/1)", 
               "[Improved Elsevier Top 100](https://data.mendeley.com/datasets/9sxdykm8s4/2)", 
               "[SDSN](https://ap-unsdsn.org/regional-initiatives/universities-sdgs/)", 
               "[CMU Top 250 Words](https://www.cmu.edu/leadership/the-provost/provost-priorities/sustainability-initiative/sdg-definitions.html)",
               "[CMU Top 500 Words](https://www.cmu.edu/leadership/the-provost/provost-priorities/sustainability-initiative/sdg-definitions.html)",
               "[CMU Top 1000 Words](https://www.cmu.edu/leadership/the-provost/provost-priorities/sustainability-initiative/sdg-definitions.html)",
               "[University of Auckland (Work in Progress)](https://www.sdgmapping.auckland.ac.nz/)", "[University of Toronto (Work in Progress)](https://data.utoronto.ca/sustainable-development-goals-sdg-report/sdg-report-appendix/)"),
  "Dataset" = c("`cmu_usc_pwg_mapped`",
             "`elsevier_keywords`",
             "`elsevier100_keywords`",
             "`sdsn_keywords`",
             "`cmu250_keywords`",
             "`cmu500_keywords`",
             "`cmu1000_keywords`",
             "`auckland_keywords`",
             "`toronto_keywords`"),
  "CSV" = c("[Link](https://github.com/USC-Office-of-Sustainability/USC-SDGmap/tree/main/Datasets/cmu_usc_pwg_mapped.csv)", "[Link](https://github.com/pwu97/SDGmapR/blob/main/datasets/elsevier_keywords_cleaned.csv)", "[Link](https://github.com/pwu97/SDGmapR/blob/main/datasets/sdsn_keywords_cleaned.csv)", 
"[Link](https://github.com/pwu97/SDGmapR/blob/main/datasets/cmu250_keywords_cleaned.csv)",
"[Link](https://github.com/pwu97/SDGmapR/blob/main/datasets/cmu500_keywords_cleaned.csv)",
"[Link](https://github.com/pwu97/SDGmapR/blob/main/datasets/cmu1000_keywords_cleaned.csv)", "", ""),
  "SDG17" = c("Yes", "No", "No", "Yes", "No", "No", "No", "Yes", "Yes")
)
kable(sdg_table)

```


## Creating / Choosing the keyword list

A keyword list for the purposes of this R package must include the following columns:
'keyword', 'goal', 'weight', 'pattern', 'color'

Each keyword has a weight representing its relevance to that SDG, and a pattern which allows our function to read capitalization and italics in the same way. We are working on finding a way to include a pattern which considers the plural and singular versions of words as the same. Each SDG already has its own color assigned by the UN.

If you would like to use the USC-CMU, CMU250, or any other keyword lists located in the Datasets folder in this repository, then no extra work is required!
<!-- skip to different section -->

If you would like to create your own keyword list with unique weights, things become a bit more difficult. At CMU, they used Google's word2vec software to establish weights for each word and sdg.
We have not come around to finding a more effective method to assign weights to these words, but check back at a later date to see our progress on this matter.

### Including your own keywords

We were motivated to use keywords from USC's PWG in combination with CMU250, so we expanded the CMU250 dataset to also include words in our list that mapped to other data sets.

In the R file named 'keyword_list_generator.R', you can find the code we used to generate our keyword list.

With this code, we added words from the PWG list (that did not have weights assigned) that were included in the CMU1000 lis using left-joins from the 'dplyr' library.

In addition, this R file has code to add a column to your initial unweighted keyword list which records the dataset each word was mapped to.

### Exclude words

At the bottom of the same R file, there is a list called 'exclude_words'. These are the words which we don't want to be included in our mapping to college course descriptions. Many of these words like "students" and "academics" would be overly mapped due to their relevance to course descriptions. This file is where you would be able to update this list as you see fit. Note: You can always use the same code chunk in other places of the code if you want to exclude at later stages and not at the very beginning.


## Cleaning up course data

At USC, we received a file called 'USC_FULL_COURSE_LIST_20182_20183_20191' which can be found in the Datasets folder. THis csv file contains data for every single course offered for 3 different semester at USC. The first thing we did was clean up the data, get rid of repeats (and add a separate columns to keep track of how many sections were offered), and rename the columns.

In the R file named 'cleaning_course_data.R', you can see code for how to clean this course data. The three functions to do these are 'clean_data', 'get_semesters', and 'transform_data' which gets the course data into a nice format. The produced course data can be found in the Datasets folder with the name 'usc_courses'.


## Mapping course descriptions to 17 SDGs

In the R file named 'mapping_course_descriptions.R', you can find code for mapping the clean course data to the 17 SDG's using loops and a function called 'tabulate_sdg_keywords' (which can be found in the file named after that function). Joining the course description keywords with their goals and weights to the chosen keyword list, this file writes out a csv file which we refer to as the 'master_course_SDG_data' which you can find in the Datasets folder. 

**Notice** that in the 'tabulate_sdg_keywords' function, there is a parameter which requires a keyword list. Ensure that when you run this code  (this may take awhile), the 'keywords' parameter is set to the keyword list of your choosing. By default, it is set to the Elsevier top 100 keywords list.

If you created your own keyword list, you need to update the body this function to account for the name of yours since you cannot pass a csv file directly into the function parameter. Look at the comments in the file and follow the example of how I added the parameter "cmu_usc" to the function. 


## Susainability related courses
With the master data, we can look into which classes are sustainability inclusive, sustainability focused, or not related to the SDGs. Classes defined as not related were not mapped to any SDGs. Sustainbility focused courses are ones which mapped to both environmental SDGs as well as economic/social ones. The criteria for these are 'environmental goals: 13, 14, 15' and 'economic goals: 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 16, 17'. The R file 'sustainability_related_classes.R' contains the code for how to do this. At the end, you can sum up the total number of sustainability focused or inclusive classes and report those numbers to Stars under AC-1 credit. 
<!-- need to change wording -->


### Finding the sum of the weights for each SDG

In the R file named 'total_weight_generator.R', you can find code that adds the sum of the weights for each SDG a course mapped to. The resulting csv file 'classes_total_weight' contains unique course titles, as well as 17 additional columns that show the combined weight of all keywords by SDG. The final column shows the total weight of all the keywords mapped from that course. 


### Filtering the data by threshold

You can filter data so that only classes above a certain threshold are met.
<!-- ask julie about whether you filter the data or the keywords -->


## Creating an RShiny app

The ShinyApp folder, contains all relevant files that pertain to creating a Shiny dashboard like the one we created. The only necessary files for the shiny app are the master course SDG data and the cleaned course data, as well as the chosen keyword list. Inside the folder, a subfolder called www stores all stylesheets and pictures for the app. 
<!-- add link -->

Step by step instructions on how to work the R shiny app are to follow...
<!-- ask julie about this, how much code do i show -->



