---
title: "README"
output: github_document
  # md_document:
  #   variant: markdown_github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# USC Sustainability Course Finder

```{r, warning=FALSE,message=FALSE,echo=FALSE}
# load all packages
library(tidyverse)
library(knitr)
```


Peter Wu at Carnegie Mellon wrote the initial code that inspired this project, and his original R package can be found on [Github](https://github.com/pwu97/SDGmapR). 
At USC, Brian Tinsley and Dr. Julie Hopper in the Office of Sustainability have been working to develop this package further and raise sustainability awareness in higher education by mapping USC course descriptions to the United Nations Sustainability Development Goals.  

Check out the [Sustainability Course Finder](https://usc-sustainability.shinyapps.io/Sustainability-Course-Finder/){target="_blank"} to see the the product of our work! Also find an article about our web app [here!](https://news.usc.edu/207748/new-usc-sustainability-course-finder/){target="_blank"}

## Table of Contents

- [Installation](#installation)
- [Keyword List](#keyword-list)
- [Cleaning Course Data](#cleaning-course-data)
- [Mapping Course Descriptions](#mapping-course-descriptions)
- [Sustainability Related Courses](#sustainability-related-courses)
- [General Education](#general-education)
- [Creating Shiny App](#creating-shiny-app)
- [Questions?](#questions)


## Installation

If you wish to install this package on your computer, clone this repository by following [these instructions.](https://docs.github.com/en/repositories/creating-and-managing-repositories/cloning-a-repository)
Once installed, you can open, view, and edit all files in this repository. 


## Keyword List

The way in which we map course descriptions to the SDGs is through keyword lists which has keywords relevant for each SDG. In prior versions of this package, we attempted to use various Python and R packages, such as [text2sdg](https://www.text2sdg.io/), to give weights to keywords based on their relevance to the goal. We have since transitioned to using *frequencies* of keywords since the varying weights were often ambiguous. With this new method, each keyword has a weight of 1. The first few rows of the USC keyword table, which has over 4200 keywords, are shown below. 


```{r, echo=F}
keywords = read.csv("data/usc_keywords.csv")
kw = keywords %>% select(goal, keyword, color) %>% (head)
kable(kw)
```

The USC keyword list has been modified many times with the help of the Presidential Working Group (PWG) and is continually being improved to increase accuracy. 

The table below lists publicly available SDG keywords that have been published online. Some
of the lists have weights associated with every keyword, while some do not. Also note that some of these keyword lists do not have keywords for SDG 17.

```{r, echo=FALSE, example}
sdg_table <- data.frame(
  "Source" = c("[USC Keywords (Work in Progress)](https://github.com/USC-Office-of-Sustainability/SustainabilityCourseFinder/blob/main/shiny_app/usc_keywords.csv)",
               "[Core Elsevier (Work in Progress)](https://data.mendeley.com/datasets/87txkw7khs/1)", 
               "[Improved Elsevier Top 100](https://data.mendeley.com/datasets/9sxdykm8s4/2)", 
               "[SDSN](https://ap-unsdsn.org/regional-initiatives/universities-sdgs/)", 
               "[CMU Top 250 Words](https://www.cmu.edu/leadership/the-provost/provost-priorities/sustainability-initiative/sdg-definitions.html)",
               "[CMU Top 500 Words](https://www.cmu.edu/leadership/the-provost/provost-priorities/sustainability-initiative/sdg-definitions.html)",
               "[CMU Top 1000 Words](https://www.cmu.edu/leadership/the-provost/provost-priorities/sustainability-initiative/sdg-definitions.html)",
               "[University of Auckland (Work in Progress)](https://www.sdgmapping.auckland.ac.nz/)", "[University of Toronto (Work in Progress)](https://data.utoronto.ca/sustainable-development-goals-sdg-report/sdg-report-appendix/)"),
  "Dataset" = c("`usc_keywords`",
              "`elsevier_keywords`",
             "`elsevier100_keywords`",
             "`sdsn_keywords`",
             "`cmu250_keywords`",
             "`cmu500_keywords`",
             "`cmu1000_keywords`",
             "`auckland_keywords`",
             "`toronto_keywords`"),
  "CSV" = c("[Link](https://github.com/USC-Office-of-Sustainability/SustainabilityCourseFinder/blob/main/shiny_app/usc_keywords.csv)",
    "[Link](https://github.com/pwu97/SDGmapR/blob/main/datasets/elsevier_keywords_cleaned.csv)", "[Link](https://github.com/pwu97/SDGmapR/blob/main/datasets/elsevier100_keywords_cleaned.csv)", "[Link](https://github.com/pwu97/SDGmapR/blob/main/datasets/sdsn_keywords_cleaned.csv)", 
"[Link](https://github.com/pwu97/SDGmapR/blob/main/datasets/cmu250_keywords_cleaned.csv)",
"[Link](https://github.com/pwu97/SDGmapR/blob/main/datasets/cmu500_keywords_cleaned.csv)",
"[Link](https://github.com/pwu97/SDGmapR/blob/main/datasets/cmu1000_keywords_cleaned.csv)", "", "")
)
kable(sdg_table)
```



## Cleaning Course Data

While I do not expect another school's data to be of the same format as the raw files at USC, I am still including some details on how we cleaned the files in hopes that it may address some common problems others might have with their data.  

<!-- add link to a file? -->
Course data was retrieved from the USC’s Office of Academic Records and Registrar, and the raw data files, as well as the R scripts to clean them, can be found in the `cleaning_raw_data` folder.
These files had lots of problems with spacing and column names, and we addressed these issues in `cleaning_scattered_files.R`.  

<!-- show the dataframe -->
<!-- show the code to clean it -->
In the `clean_file` function, we loop from the bottom of the raw dataframe and combine empty rows with the row above to fix the empty line issue.
We also trim spaces before and after to account for random spaces added at the end of some data entries. One problem to look out for when cleaning a dataframe is accounting for empty values ("") vs NA vs "NA" in data entries.

```{r eval=FALSE}
# go through backwords and combine error rows with row above it
for(i in seq(nrow(x), 2, -1)) { # Work on the table in bottom to top so we can merge the values
  if(is.na(x[i, "SECTION"]) | x[i, "SECTION"] == "NA" | x[i, "SECTION"] == "") { #always note if values are NA or "NA" or ""
      x[i, "SECTION"] = NA # fix the issue of combining character "NA" 
      print(i)
      # Work on the current row and the previous row.
      # Don't modify numeric columns (don't want to merge NA values).
      # Use lead() to check across rows, and turn NA values into an empty string.
      # Use paste() to combine the row values.
      # use trim() to get rid of any excess white space produced.
      x[i-1,] <- (x[c(i-1,i),] %>% mutate(across(.fns = ~ ifelse(is.numeric(.x), .x, trim(paste(.x, ifelse(is.na(lead(.x)), "", lead(.x))))))))[1, ]
    }
}
```

Once the files are cleaned, we run a function (in the same R script) to clean each individual file and write it as CSV into a new folder, as well as obtain the "origin" column which is the year and semester of the data. Once again, I do not expect anyone's data to be in the same format, but this might help someone combine scattered CSV files of different formats. 

```{r eval=FALSE}
# make sure folder only contains CSVs you want to run the code on
files = list.files("SOC_files/")

# going to apply the function to each file and write a new csv in "clean_data" folder
# this loop will also get the "origin" column from the file name
# other users may have different file names and have to figure out how to get the origin
# column in the form "YYYYS" where s is 1, 2, 3 for spring, summer, fall
for (i in 1:length(files)){
  table = read.csv(paste0("SOC_files/", files[i]), header=TRUE) # load file
  out <- clean_file(table) # clean the file
  out$origin = NA #create origin column
  file_name = files[i] #grab the name of the file that starts with YYYYS
  term = substr(file_name, 1, 5) # grab just the first 5 digits to be used in the origin
  out$origin = term
  name = paste0("clean_data/", term, ".csv") # will change this to actually be the year output format
  write.csv(out, file = name, row.names = FALSE)
}
```

In the next R file, `cleaning_2020-2023.R`, we read in the combined clean CSV and reformat it.
We change column names, count the number of students and sections for each section, cut out research courses, and we create the "semester," "all_semesters," and "course_level" columns. To see this code please see the R script. 

There is an R script in the same directory that shows you how to add a course to the dataframe `adding_course.R`. All you need to remember for adding a course in this way is that you include ALL COLUMNS when adding new entries -- otherwise the data will be messy. 


## Cleaning Course Descriptions

Once we have the cleaned dataframe with correct column names, we now clean the course descriptions to increase the accuracy of the mapping we will perform to the keyword list.
If you navigate to `cleaning_course_descriptions.R`, you will see what appears to be a daunting 600-line R script -- do not be scared.
This file corrects context-dependency issues that lead to inaccurate mappings of courses to SDGs. For example, courses with the phrases "business environment" or "learning environment" should not be mapped to the word "environment" and its related SDGs. 

The first thing we do is create a new column "clean_course_desc" which holds the course description of the class but **excluding punctuation.** By exluding punctuation (except for apostraphes), we ensure there are no problems mapping words that come before a comma or period or other punctuation. Code to achieve this is shown below:

```{r eval=FALSE}
# column to hold cleaned course description
usc_courses["clean_course_desc"] = NA

# put the clean version of course_desc in new column without punctuation, except for '
for (i in 1:nrow(usc_courses)){
  desc = usc_courses$course_desc[i]
  desc_clean = gsub("[^[:alnum:][:space:]']", " ", desc)
  desc_spaces = str_squish(desc_clean)
  usc_courses$clean_course_desc[i] = desc_spaces
}
```

To account for context dependencies either before a word or after a word, follow the model in the file, and ensure to convert words to lowercase and trim whitespace. 

## Mapping Course Descriptions

Now, we are ready to map the clean course descriptions void of punctuation errors and major context dependencies to our keyword list and the SDGs. 
In the `R` directory, find the code to map course descriptions in `mapping_course_descriptions.R`.  

The following function `find_words` is the foundation for the mapping. Given some text, one of the 17 SDGs, and a keyword list, it returns a vector of all keywords in the text that map to the designated SDG (including repeats). 

```{r eval=TRUE}
# goal of this function is to return a vector of all the keywords 
# in a course description (including duplicates)
find_words = Vectorize(function(text, sdg, keywords="usc_keywords", count_repeats=FALSE){
  if (keywords=="usc_keywords"){
    sdg_keywords = usc_keywords %>% filter (goal==sdg)
  }
  
  patterns <- sdg_keywords$pattern
  keywords <- sdg_keywords$keyword
  
  words <- c()
  
  for (i in 1:nrow(sdg_keywords)){
    if (grepl(tolower(patterns[i]), tolower(text))){
      # count number of times
      sum = str_count(tolower(text), patterns[i])
      for (j in 1:sum){
        words = c(words, keywords[i])
      }
    }
  }
  return(words)
})
```


Here is an example of how it works:

```{r}
usc_keywords = read.csv("data/usc_keywords.csv")
find_words("this maps to SDG 1 because the words poverty and charity and charity", 1)
```

Now that the function to map text is created, we can use a loop to go through the entire course dataframe for each of the 17 sdgs and find the keywords. The following function performs the mapping and creates the "goal" and "keyword" columns. Note: this function can take a very long time to run (about 3-4 hours for the USC keywords and course dataframe).

```{r, eval=FALSE}
# read in the USC course data
classes = read.csv("usc_courses_cleaned.csv")

all_sdg_keywords <- data.frame() # new dataframe to hold everything
for (goal_num in 1:17) {
  print(goal_num) #useful for seeing how far you are in the code run
  classes %>%
    mutate(goal = goal_num, #run on clean_course_desc column w no punctuation and accuracy edits made
           keyword = find_words(classes$clean_course_desc, goal_num, keywords = "usc_keywords")) %>%
    unnest(keyword) -> cur_sdg_keywords
  
  all_sdg_keywords <- rbind(all_sdg_keywords, cur_sdg_keywords) 
}
```

Once the mapping is done, it is a good idea to save the dataframe as a .Rda object so you don't need to rerun it every time.

```{r, eval=FALSE}
save(all_sdg_keywords, file="all_sdg_keywords.Rda")
```

Before writing the dataframe as a CSV, we also want to combine this output with the keyword dataframe to obtain the color and weight columns. Remember to add all relevant columns to the select() function. 

```{r, eval=FALSE}
#now join it with usc_keywords to get color and weight
all_sdg_keywords %>%
  left_join(usc_keywords, by = c("goal", "keyword")) %>%
  select(courseID, course_title, section, semester, keyword, goal, weight, color, course_desc, clean_course_desc, department, N.Sections, year, course_level, total_enrolled, all_semesters) %>%
  arrange(courseID) -> all_sdg_keywords
```


## Sustainability Related Courses

With the mapping complete, we can refer to the R script `sustainability_related_classes.R` which analyzes the goals a class mapped to and labels it as "SDG-related", "sustainability-focused", or "not related".
We first make a new dataframe of unique courseID's, and then create the columns "all_goals" and "sustainability_classification". 
To obtain all mapped goals for each class, use the following code:

```{r, eval=FALSE}
index = 1
for (course in sustainability$courseID){
  # subset master data to just the rows for that class and grab the unique goals
  mini_df = unique(master_data[master_data$courseID == course, "goal"])
  # combine all the goals into a string to be added to the goals column in df
  goals = paste(mini_df, collapse=",")
  #update the goals column of df to be this string "goals"
  sustainability$goals[index] = goals
  index = index + 1
}
```

We have tried multiple methods to determine sustainability classifications, and our current method is as follows:  

* If a course's description does not map to any SDGs (no keywords in the master data) or only contains one keyword, it is "NotRelated".  
* If a course description contains two or more keywords, we categorize it as "SDG-Related".  
* If a course maps to at least one social/economic SDG (SDGs 1-12, 16, 17) and one environmental goal (13, 14, 15), then it is labeled "Sustainability Focused".  

Code for achieving these labels are found in the R script.  

Lastly, we want to join this dataframe with the course data, so we run the following code:

```{r, eval=FALSE}
# "sustainability" is the dataframe we just made, usc_courses is the cleaned USC course data
course_data = usc_courses %>% left_join(sustainability, by="courseID")
write.csv(course_data, "usc_courses_full.csv", row.names = F)
```

## General Education

We were given completely a different set of data for USC's general education requirements. Code for obtaining the GE categories and course titles is found in `general_education.R`. In this script, we join the GE data with the course / sustainability data and then go through and ensure that unmapped classes have "Not Related" as the sustainability classification. The resulting dataframe is used in the Shiny App for the general education page. 

## Creating Shiny App

When I was tasked with creating a shiny app, I was daunted but eventually learned through trial and error. Despite the scary sight of 1400 lines of code, I can assure that anyone using this github repository can replicate the shiny app with little to no coding experience. To learn the basics, refer to [this tutorial.](https://rstudio.github.io/shinydashboard/)   

If you follow along with the code in the `app.R` file in the "shiny_app" directory, you will understand the structure and functionality of a shiny app. 


## Questions?

There have been many packages in R that have confused me, and I am very grateful for some developers that responded to my emails and helped me along the way.  

If you have any questions, comments, or concerns, please reach out to me via email: [btinsley@usc.edu](mailto:btinsley@usc.edu)

